Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Added to Conclusions.

>>>>

If time had permitted it would have been beneficial to analyze the effect of different
data chunk sizes on the overall performance of the dynamic scheduler, including having
different data chunk sizes for each device, based on computational power.  We could have
also included a ratio-based dynamic scheduler which would have pulled a percentage of the
remaining data from the work-queue instead of a set static amount of data.  This would have
alleviated the problem of not having enough work to do at the outset of the problem, while
still retaining fine-grained distribution of data near the end of the queue.  The lack of
this sort of analysis limits our overall ability to throughly analyze the performance
of the dynamic scheduler.
